\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-22 src/tex/ms.tex
Add some headers

Every waveform approximants have some fitting parameters that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of
IMRPhenomD, there are $\sim 220$ \kw{Kelvin check number} fitting parameters
used to capture the behavior of the amplitude and phase as a function of the
mass ratio and spins.

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{../static/amplitude_loss.pdf}
    \caption{ Relative error of amplitudes of IMRPhenomD waveforms. Blue: Error
        between original Phenom waveform and NR waveform; Orange: Error between
        optimized waveform and NR waveform. }
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{../static/MM_logdiff_q148.pdf}
    \caption{ Distribution of the log difference of mismatches between optimized
        and original model. The mean shows a 36\% decrease in mismatch. }
\end{figure}

>>>>

Every waveform approximants have some fitting parameters that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of
IMRPhenomD, there are $\sim 220$ \kw{Kelvin check number} fitting parameters
used to capture the behavior of the amplitude and phase as a function of the
mass ratio and spins. \kw{Say something about how the fitting parameters affect the accuracy of the waveform model}

% Motivation
\kw{Motivate the need for improving the fitting process by joint fit.}

% How the fitting process is done now.
\kw{Mention how these parameters are often hand tuned.}

Since we can differentiate through the entire waveform model against the fitting
parameters, one can use gradient descent to find the optimal fitting parameters
all at once instead of fitting them in subsets.

\kw{Describe figure loss_compare}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{../static/amplitude_loss.pdf}
\caption{ Relative error of amplitudes of IMRPhenomD waveforms. Blue: Error
    between original Phenom waveform and NR waveform; Orange: Error between
    optimized waveform and NR waveform. }
\label{fig:loss_compare}
\end{figure}

\kw{Describe figure logdiff}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{../static/MM_logdiff_q148.pdf}
\caption{ Distribution of the log difference of mismatches between optimized
    and original model. The mean shows a 36\% decrease in mismatch. }
\label{fig:MM_logdiff}
\end{figure}

\kw{Describe implication}

% Implication
